Streaming Slot Extraction for Wikipedia Entities

### 2013-11-10 paper/flairs27/content/results.tex
merge

\caption{Recall Measure: Generic slot names like affiliate had the most recall, compared to less popular slot names e.g. DateOfDeath}
\centering
\label{table:finalresultrecall}
\begin{tabular}{|l|c|c|}
\hline 
 \textbf{Slot Name} & \textbf{Instances Found} & \textbf{Entity Coverage} \\ 
\hline 
Affiliate & 108598 & 80 \\ \hline 
AssociateOf & 25278 & 106 \\ \hline 
AwardsWon & 38 & 14 \\ \hline 
CauseOfDeath & 0 & 0 \\ \hline 
{\tiny Contact\_Meet\_Entity} & 191 & 8 \\ \hline 
{\tiny Contact\_Meet\_PlaceTime} & 5974 & 109 \\ \hline 
DateOfDeath & 87 & 14 \\ \hline 
EmployeeOf & 75 & 16 \\ \hline 
FoundedBy & 326 & 30 \\ \hline 
FounderOf & 302 &  29 \\ \hline 
Titles & 26823 & 118 \\ \hline 
TopMembers & 314 & 26 \\ \hline

@@

\caption{Accuracy Measure: Accuracy of AffiliateOf was the best and Affiliate applied poorly due to ambiguity of being an affiliate of somebody/something}
\centering
\label{table:finalresultaccuracy}
\begin{tabular}{|l|c|c|p{13mm}|}
\hline 
 \textbf{Slot Name}  & \textbf{Correct} & \textbf{Wrong Entity} & {\small \textbf{Incorrect Value}} \\ 
\hline 
Affiliate & 1\% & 95\% & 5\% \\ \hline 
AssociateOf & 63.6\% & 9.1\% & 27.3\%  \\ \hline 
AwardsWon & 10\% & 10\% & 80\%  \\ \hline 
CauseOfDeath & 0\% & 0\% & 0\%  \\ \hline 
{\tiny Contact\_Meet\_Entity} & 21\% & 42\% & 37\%  \\ \hline 
{\tiny Contact\_Meet\_PlaceTime} & 5\% & 20\% & 85\%  \\ \hline 
DateOfDeath & 29.6\% & 71\% & 25\%  \\ \hline 
EmployeeOf & 5\% & 30\% & 65\%  \\ \hline 
FoundedBy & 62\% & 17\% & 21\%  \\ \hline 
FounderOf & 50\% & 0\% & 50\%  \\ \hline 
Titles & 55\% & 0\% & 45\%  \\ \hline 
TopMembers & 33\% & 17\% & 50\%  \\ \hline

>>>>

\caption{Recall Measure: Generic slot names like affiliate had the most recall, compared to less popular slot names e.g. DateOfDeath}
\centering
\label{table:finalresultrecall}
\begin{tabular}{|l|p{13mm}|p{22mm}|}
\hline 
 \textbf{Slot Name} & \textbf{Instances Found} & \textbf{Entity \hspace{5 mm} Coverage} \\ 
\hline 
Affiliate & 108598 & 80 \\ \hline 
AssociateOf & 25278 & 106 \\ \hline 
AwardsWon & 38 & 14 \\ \hline 
CauseOfDeath & 0 & 0 \\ \hline 
Contact\_Meet\_Entity & 191 & 8 \\ \hline 
Contact\_Meet\_PlaceTime & 5974 & 109 \\ \hline 
DateOfDeath & 87 & 14 \\ \hline 
EmployeeOf & 75 & 16 \\ \hline 
FoundedBy & 326 & 30 \\ \hline 
FounderOf & 302 &  29 \\ \hline 
Titles & 26823 & 118 \\ \hline 
TopMembers & 314 & 26 \\ \hline

@@

\caption{Accuracy Measure: Accuracy of AffiliateOf was the best and Affiliate applied poorly due to ambiguity of being an affiliate of somebody/something}
\centering
\label{table:finalresultaccuracy}
\begin{tabular}{|l|p{10mm}|p{10mm}|p{11mm}|}
\hline 
 \textbf{Slot Name}  & \textbf{Correct} & \textbf{Wrong Entity} & {\small \textbf{Incorrect Value}} \\ 
\hline 
Affiliate & 1\% & 95\% & 5\% \\ \hline 
AssociateOf & 63.6\% & 9.1\% & 27.3\%  \\ \hline 
AwardsWon & 10\% & 10\% & 80\%  \\ \hline 
CauseOfDeath & 0\% & 0\% & 0\%  \\ \hline 
Contact\_Meet\_Entity & 21\% & 42\% & 37\%  \\ \hline 
Contact\_Meet\_PlaceTime & 5\% & 20\% & 85\%  \\ \hline 
DateOfDeath & 29.6\% & 71\% & 25\%  \\ \hline 
EmployeeOf & 5\% & 30\% & 65\%  \\ \hline 
FoundedBy & 62\% & 17\% & 21\%  \\ \hline 
FounderOf & 50\% & 0\% & 50\%  \\ \hline 
Titles & 55\% & 0\% & 45\%  \\ \hline 
TopMembers & 33\% & 17\% & 50\%  \\ \hline
